TUDataset: A collection of benchmark datasets for learning with graphs

### 2020-05-09 main.tex
Work on GNN evaluation code. ++
MC.

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    & \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
		& \text{GraphSage} &          \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			\bottomrule
	\end{tabular}}
\end{table*}

@@

\onecolumn
\section{Evaluation Method Examples}
\lstinputlisting[language=Python]{example.py}

>>>>

			& \multirow{3}{*}{\vspace*{4pt}\textbf{Method}}&\multicolumn{6}{c}{\textbf{Dataset}}\\\cmidrule{3-8}
			& & {\textsc{Enyzmes}}         &  {\textsc{Imdb-Binary}}      & {\textsc{Imdb-Multi}}           & {\textsc{NCI1}}       & {\textsc{Proteins}}           & {\textsc{Reddit-Binary}}     \\	\toprule
			\multirow{4}{*}{\rotatebox{90}{Kernel}}	& \text{1-WL}  &    \scriptsize $\pm  \pm  $       & \scriptsize $\pm   \pm $ &  \scriptsize $\pm  \pm   $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm  \pm   $ & \scriptsize $\pm  \pm $  \\
				& \text{2-LWL} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{2-LWL$^+$} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{WLOA} &   \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
				& \text{GR}            &     \scriptsize $\pm  \pm$       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm   $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm \pm $ & \scriptsize $\pm  \pm  $   \\
				& \text{SP}            &   \scriptsize $\pm  \pm $       &  \scriptsize $\pm  \pm  $ &  \scriptsize $\pm  \pm $ &  \scriptsize $\pm \pm  $  & \scriptsize $\pm  \pm $ &  \scriptsize $\pm\pm $  \\
			\cmidrule{2-8}	
			\multirow{2}{*}{\rotatebox{90}{GNN}}	& \text{GIN-$\varepsilon$}    & \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
		& \text{GIN-$\varepsilon$-JK} &          \scriptsize $\pm \pm $       &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $ & \scriptsize $\pm   \pm $ &  \scriptsize $\pm \pm $ &  \scriptsize $\pm  \pm  $   \\
			\bottomrule
	\end{tabular}}
\end{table*}

eintragen
IMDB-BINARY GINWithJK 72.93333333333334 0.5185449728701322 4.122566622330749
IMDB-BINARY GIN 72.06666666666668 0.3091206165165233 4.024370206076419
IMDB-MULTI GINWithJK 50.644444444444446 1.01153837126587 4.59462917806765
IMDB-MULTI GIN 48.84444444444444 0.37051848890073463 3.523185988018918
NCI1 GINWithJK 79.67558799675588 0.4130683399269047 1.5714739782362184
NCI1 GIN 78.01297648012977 0.38333502994634977 1.9142541830162463
PROTEINS GINWithJK 71.27895752895752 0.9574183044143284 4.459876910576175
PROTEINS GIN 71.16527241527241 0.3211668436757545 3.612551907408368
REDDIT-BINARY GINWithJK 90.31666666666668 0.4326918328582383 1.9894862541760765

REDDIT-BINARY GIN 90.18333333333334 0.39228674319799567 2.169805418823438

ENZYMES WL1 50.28333333333334 1.1524129275375015 6.872065030089411
ENZYMES LWL2 55.6 1.5709162223930901 6.788552455748164
ENZYMES LWLP2 53.55 1.5402921800749356 6.3274314606235675
ENZYMES WLOA 56.7 2.0094222497468714 7.129671957546308
ENZYMES GR 32.35 1.036688102672266 5.359804100897718
ENZYMES SP 39.8 1.2840906856172143 6.473364229243128
IMDB-BINARY WL1 72.57 0.9143850392476894 4.133412633647891
IMDB-BINARY LWL2 73.37 0.6372597586541924 4.430925411243119
IMDB-BINARY LWLP2 76.65 1.353698637068088 4.924175057814253
IMDB-BINARY WLOA 72.69 0.6818357573492301 4.749094650562357
IMDB-BINARY GR 59.19 0.865390085452797 5.017359863513877
IMDB-BINARY SP 57.860000000000014 1.4291256067959874 5.734143353631822
IMDB-MULTI WL1 50.09333333333333 0.6262409901769259 3.811118237764636
IMDB-MULTI LWL2 50.15333333333333 0.38418745424597134 4.055016098063676

IMDB-MULTI LWLP2 74.01333333333334 0.9360911636516311 4.502818870194288
IMDB-MULTI WLOA 49.86666666666666 0.6352602266438174 4.455209185760966
IMDB-MULTI GR 39.17333333333333 0.7660577291852385 4.380887784202853
IMDB-MULTI SP 39.50666666666666 0.18184242262647857 3.3791780723194287
NCI1 WL1 84.38929440389293 0.25125704415427325 1.6049986739634532
NCI1 LWL2 84.89537712895375 0.20028336376892103 1.7608176856505284
NCI1 LWLP2 84.32846715328466 0.35931558467907326 1.9074851647350406
NCI1 WLOA 84.985401459854 0.26237917572915365 1.944431716559596
NCI1 GR 65.8272506082725 0.31011161731748405 2.3057620215984294
NCI1 SP 74.21411192214111 0.26335881513838716 2.007846272147655
PROTEINS WL1 73.49348455598457 0.6459030975700468 4.234672201391122
PROTEINS LWL2 74.79681467181469 0.665180097352863 4.60334576380455
PROTEINS LWLP2 75.63296332046333 0.5832232093036747 4.118575468095003
PROTEINS WLOA 73.48656692406692 0.6497356451647441 4.4435644964869745
PROTEINS GR 71.91473616473615 0.5582152728034838 4.153766329154282
PROTEINS SP 75.29930823680823 0.433922307671726 3.6869730552272064
REDDIT-BINARY WL1 73.15 0.5860887304837047 3.1547583108694712
REDDIT-BINARY LWL2 89.09 0.4856953777832335 2.504376169827528

@@

\onecolumn
\section{Evaluation Method Examples}
\lstinputlisting[language=Python]{example.py}
\cm{Add linear svm and GNN example}
